\documentclass[
    a4paper,
    12pt,
    parskip=half,
    headings=standardclasses,
    footskip=0pt,
    footlines=1,
    headheight=80in
]{scrartcl}

\sloppy
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{microtype}

\usepackage{amsmath,amssymb,amsthm}
\usepackage{minted}

\usepackage{hyperref}
\usepackage{tcolorbox}

\usepackage{newpxtext,newpxmath}

\newcommand{\lgrey}{black!5}

\begin{document}

\begin{center}
    {\LARGE\textbf{Bidding Game Challenge}}\\[6pt]
    Time limit: 10 seconds, Memory limit: 50 MB\\
    {\small Deadline for submissions: \textbf{2023-11-30}}
\end{center}

\paragraph*{Problem}

For this challenge, you will be playing a round-based auction game against all
other participants simultaneously.

You start off with $10^5$ coins. In each round, you bid a number of coins.
Of course, you may only bid at most the amount of coins you have left.
Everyone loses the number of coins they bid.
The player with the highest bid wins the round and gets 1 point. In case of a tie, all participants with the highest bid
split the point evenly.

You only know the bids of your opponents after you have made your bid.

After $10^3$ rounds, all players are ranked by the
number of points they earned (see \hyperref[scoring]{Scoring} for more details).

There will be 3 passes of the game as some solutions may use
randomized strategies.

\paragraph*{Interaction} All interaction is done via standard input and output.

The first line of input contains a single integer $n$ ($1 \leq n \leq 10^3$),
the number of opponents.

Then for each round, you submit a bid by printing a single integer $b$ ($0 \leq
    b \leq 10^5$) to standard output\footnote{Remember to flush the output!}. After
making a bid, you will receive a line of input containing $n$ space separated
integers $b_1, \ldots, b_n$ ($-1 \leq b_i \leq 10^5$), the bid of your $i$-th
opponent. A bid of $-1$ means that the opponent made an invalid bid or hit the
time or memory limit. You are not required to read in the bids of your opponents after
making your last bid.

If you make an invalid bid or hit the time or memory limit, you will be
disqualified for the rest of the game. Your earned points will still remain valid.

See \hyperref[sample-programs]{Sample Programs} for an exemplary implementation.

\paragraph*{Example interaction} Below is an example interaction between four participants over three rounds
each starting with $6$ coins. On the left is the input given to the program, on the right is the output of the program.

\begin{tcolorbox}[colback=\lgrey,fontupper=\small\ttfamily]
3

\hfill0

2 2 4

\hfill4

2 3 -1

\hfill2

2 1 -1
\end{tcolorbox}

\textit{Explanation.} In the first round, the bids are $2$, $2$, $4$ and $0$. Therefore opponent $3$ wins the round and gets $1$ point.
In the second round, the bids are $2$, $3$ and $4$, so we win. Opponent $3$ made an invalid bid and is disqualified from now on.
In the third and final round, the bids are $2$, $1$ and $2$, so we win together with opponent $1$ and get half points each.
Opponent $3$ remains disqualified.

So we win with $1.5$ points in total followed by opponent $3$ with $1$ point, opponent $2$ with $0.5$ points and opponent $1$ with $0$ points.

\clearpage

\subsection*{Appendix}

\paragraph*{Sample programs}\label{sample-programs}

Here are two sample programs that play the game using a simple random and ``copy the
winner'' strategy.

\begin{minted}[bgcolor=\lgrey,fontsize=\small]{python}
# rand.py
import random
n = int(input())
coins = 10**5
rounds = 10**3

for round in range(rounds):
    my_bid = random.randint(0, coins)
    coins -= my_bid
    print(my_bid, flush=True)
    
    other_bids = [int(x) for x in input().split()]
\end{minted}

\begin{minted}[bgcolor=\lgrey,fontsize=\small]{cpp}
// copycat.cpp
#include <bits/stdc++.h>
using namespace std;

int main() {
    cin.tie(0)->sync_with_stdio(0);
    int n; cin >> n;
    int coins = 1e5, rounds = 1e3;
    vector<int> other_bids(n);
    for (int round = 0; round < rounds; round++) {
        int my_bid = clamp(
            *max_element(other_bids.begin(), other_bids.end()),
            0,
            coins
        );
        coins -= my_bid;
        cout << my_bid << endl;
        for (int &bid : other_bids) cin >> bid;
    }
}
\end{minted}

\paragraph*{Scoring}\label{scoring}

Submissions are ranked by the following criteria, in order:
\begin{enumerate}
    \item The number of points.
    \item The number of rounds being not disqualified.
    \item The number of coins left.
\end{enumerate}
All numbers are calculated as the sum over all passes.

\paragraph*{System Details} All submissions are run on a single machine with the
following specifications:
\begin{itemize}
    \item Intel i7-11370H or better
    \item 16 GB RAM or more
    \item Debian GNU/Linux 12 (bookworm)
\end{itemize}

You may submit your solution as a single source file up to $64$ kB in any of the following
languages:
\begin{enumerate}
    \raggedright
    \item C++ 20 (g++ 10.2.1)\\[4pt]compiled as \texttt{g++ -std=gnu++20 -x c++ -Wall -O2 -static -pipe -o \$1 "\$1.cpp" -lm}
    \item Python 3.7.10 (PyPy 7.3.5)\\[4pt]run as \texttt{pypy3 \$1}
\end{enumerate}
You may only use the standard library of your chosen language.
You may not use
\begin{enumerate}
    \item any other libraries or packages.
    \item any other files or resources.
    \item any form of inter-process communication.
    \item the internet.
\end{enumerate}

\end{document}
